---
title: "Web Scraping in R"
format: pdf
editor: visual
---

-   In R, web scraping is done with `rvest`.

-   Some websites will offer an API, a set of structured HTTP requests that return data as JSON. Should be using API where possible. Will give more reliable data.

**Load Packages**

-   Use inspect element, or a chrome extension to get the html categories

```{r}
pacman::p_load(tidyverse, rvest)
```

```{r}
link <-
  "" #webpage 
page <- 
  read_html(link) #gets the html code from the webpage
```

```{r}
name <-
  page |>
  html_node("") |>
  html_text()

publications <-
  page |>
  html_node("") |>
  html_text
```

\newpage

## References:

-   Wickham, H, Çetinkaya-Rundel, M & Grolemund, G 2023, *R for Data Science (2e): Web scraping*, viewed 18 August 2026, [https://r4ds.hadley.nz/webscraping.html](https://r4ds.hadley.nz/webscraping.html?utm_source=chatgpt.com)

-   Motgi, A 2021, *Web Scrape Text from ANY Website -- Web Scraping in R (Part 1)*, YouTube video, Dataslice, viewed 18 August 2026, [https://www.youtube.com/watch?v=v8Yh_4oE-Fs](https://www.youtube.com/watch?v=v8Yh_4oE-Fs&utm_source=chatgpt.com).

-   Tures, J. (n.d.) \'Scraping of multi-page websites\', *Web Scraping using R*. Available at: [https://jakobtures.github.io/web-scraping/rvest3.html](https://jakobtures.github.io/web-scraping/rvest3.html?utm_source=chatgpt.com) (Accessed: 18 August 2026).
